\Title

### 2020-02-10 manuscript/manuscript.tex
Improve description of variable depth

The depth of the point sources can be chosen following different criteria.
Deep sources generate low frequencies, while shallow ones generate high
frequencies (cite).
The most simple option is to locate all point sources at the same depth, which
we will call \emph{constant depth} in the future.
If the measurement where taken at significantly different altitudes, the
elevated computation points will be more distant to the sources than the lower
ones.
This may create problems on reproducing high frequencies on the elevated
points.

One possible solution is to locate each source bellow its corresponding
observation point or block-median point at a constant \emph{relative depth}
from it.
The sources won't be all at the same depth, but they will all be at the same
distance from their corresponding observation point or block-median point.
It worth mention that this approach could not be applied to \emph{grid
sources}.

In case our survey presents heavily clustered data points, we may want to
reduce the depth of the sources bellow that region in order to reproduce the
high frequencies measured by these clustered observation points.
We can propose a \emph{variable relative depth} approach that locates each
point source to a depth proportional to the mean distance to its $k$ nearest
source neighbours \citep{cordell1992, guspi2004, guspi2009}.
We propose to add a static shift to the computed depth in order to prevent very
shallow sources in case the mean distance to the $k$ nearest neighbours is too
small.
In summary, the depth of the sources can be set as follows:

\begin{equation}
    \textrm{depth} =
        \textrm{depth factor} \cdot \textrm{mean distance}
        + \textrm{static shift}
\end{equation}

\noindent where the \emph{depth factor} and the \emph{static shift} are
parameters and the \emph{mean distance} is the mean distance to the $k$
nearest source neighbours.

>>>>

The depth of the point sources can be chosen following different criteria.
Deep sources generate low frequencies, while shallow ones generate high
frequencies (cite).
The most simple option is to locate all point sources at the same depth, which
we will call \emph{constant depth} in the future.
If the measurement were taken at significantly different altitudes, the
elevated computation points will be more distant to the sources than the lower
ones.
This may create problems on reproducing high frequencies on the elevated
points.

One possible solution is to locate each source bellow its corresponding
observation point or block-median point at a constant \emph{relative depth}
from it.
The sources won't be all at the same depth, but they will all be at the same
distance from their corresponding observation point (or block-median point).
It worth mention that this approach could not be applied to \emph{grid
sources}.

In case our survey presents heavily clustered data points, we may want to
reduce the depth of the sources bellow that region in order to reproduce the
high frequencies measured by these clustered observation points.
We can propose a \emph{variable depth} approach: it locates each point source
according to the \emph{relative depth} approach and then add a term
proportional to the mean distance to its $k$ nearest neighbour sources.
So, the depth of the sources can be computed as follows:

\begin{equation}
    \begin{split}
        \textrm{depth} =
           &\textrm{data point height} - \textrm{relative depth} \\
           &- \textrm{depth factor} \cdot \textrm{mean distance}
    \end{split}
\end{equation}

\noindent where \emph{data point height} is the elevation of the corresponding
observation (or block-median) point to the source, \emph{depth factor} and
\emph{relative depth} are parameters and \emph{mean distance} is the mean
distance to the $k$ nearest source neighbours.

Similar approaches for setting sources at depths that depend
on the distance to their nearest neighbours were already proposed by
\citet{cordell1992, guspi2004, guspi2009}.
